### 2018-12-12 chapters/2-methods.tex
figs

>>>>

\begin{figure}[!h]
    \centering \includegraphics[width=1.0\textwidth]{figures/fig1}
    \caption{{\bf The post-processing pipeline.}
    The T₂-weighted imaging (T₂w) data set is standardized, while the
    monoexponential and kurtosis models are applied to diffusion weighted
    imaging (DWI) data set. The T₂ relaxation values are obtained using a two
    parameter monoexponential function. Subsequently, the features are
    calculated using T₂w and parametric maps. The feature selection is performed
    by choosing 1\% of the features with highest AUC\@. Then with the selected
    features a logistic regression model is fitted and used to predict the
    lesion's Gleason score group.}%
    \label{fig:pipeline}
\end{figure}

\begin{figure}[!h]
    \centering \includegraphics[width=1.0\textwidth]{figures/fig2}
    \caption{{\bf An example case with parametric maps.}
    A:~Whole mount prostate histological section.
    B:~ADCₘ. C:~ADCₖ. D:~K. E:~T₂w. F:~T₂.
    This is from patient \#43 in Table~S1. The two lesions are outlined; their
    Gleason scores are 4+3 (lower, posterolateral region) and 3+4 (upper,
    anterior region).}%
    \label{fig:pmap}
\end{figure}
